Fast, Scalable Phrase-Based SMT Decoding

### 2016-02-03 acl.2016/acl2016.tex
acl paper

We also note that distortion limit which constrains hypothesis extension is dependent on the hypothesis' coverage vector, $C$ \emph{and} the end position of most recent source word that has been translated, $e$. The distortion limit must be checked for every instance of a hypothesis and translation rule, Figure~\ref{algo:Hypothesis Expansion with Unsorted Stack}.
\begin{figure} [h]
\begin{algorithmic}
%\REQUIRE source sentence $s$, translation options
\FORALL{ $hypo$ in $stack_{|C|}$} 
  \FORALL{ translation rules}
      \IF {can-expand($C(hypo)$, $e(hypo)$, translation rule range)}
	\STATE expand hypo with translation rule $\rightarrow$ new hypo
	\STATE add new hypo to next stack
      \ENDIF
  \ENDFOR % { translation options}
\ENDFOR % { hypothesis in $stack_i$} 
\end{algorithmic}
\caption{Hypothesis Expansion with Unsorted Stack}
\label{algo:Hypothesis Expansion with Unsorted Stack}
\end{figure}
However, by separating hypotheses into \emph{'ministacks'} according to coverage and end position, the distortion limit only needs to be checked for each ministack, Figure~\ref{algo:Hypothesis Expansion with Sorted Stack}.
\begin{figure} [h]
\begin{algorithmic}
%\REQUIRE source sentence $s$, translation options
\FORALL{ $ministack_{C, e}$ in $stack_{|C|}$} 
  \FORALL{ translation rules}
    \IF {can-expand($C$, $e$, translation rule range)}
      \FORALL{ $hypo$ in $ministack_{C, e}$} 
	\STATE expand hypo with translation rule $\rightarrow$ new hypo
	\STATE add new hypo to next ministack
      \ENDFOR
    \ENDIF
  \ENDFOR % { translation options}
\ENDFOR % { hypothesis in $stack_i$} 
\end{algorithmic}
\caption{Hypothesis Expansion with Sorted Stack}
\label{algo:Hypothesis Expansion with Sorted Stack}
\end{figure}
We therefore looked at the effects of three stack configurations.
\begin{enumerate}
  \item coverage cardinality,
  \item coverage,
  \item coverage and end position of most recent translated source word.
\end{enumerate}
We therefore looked at the effects of three stack configurations.
\begin{enumerate}
  \item coverage cardinality,
  \item coverage,
  \item coverage and end position of most recent translated source word.
\end{enumerate}
Table~\ref{tab:stack-configuration-model-score} present the average model on the held out test set, while Table~\ref{tab:stack-configuration-time} presents the decoding time.
\begin{table}[h]
\small
\begin{center}
\begin{tabular}{|r|p{12mm}|p{12mm}|p{13mm}|} \hline
Pop-limit	& Coverage \newline cardinality	& Coverage	& Coverage \newline \& end pos \\ \hline
100  		& -8.64513 			& ???	& -8.64513 \\
500		& -8.59563			& ??? 	& -8.59612 \\
1,000	 	& -8.5870			& ???	& -8.5870 \\ 
5,000 		& -8.58165			& ???	& -8.58098 \\ 
10,000 		& -8.58133			& ???	& -8.58015 \\ \hline
\end{tabular}
\end{center}
\caption{Average model scores for different stack configurations}
\label{tab:stack-configuration-model-score}
\end{table}

\begin{table}[h]
\small
\begin{center}
\begin{tabular}{|r|p{12mm}|p{12mm}|p{13mm}|} \hline
Pop-limit	& Coverage \newline cardinality	& Coverage	& Coverage \newline \& end pos \\ \hline
100  		& 73 			& ???	& 72 \\
500		& 237			& ??? 	& 229 \\
1,000	 	& 416			& ???	& 423 \\ 
5,000 		& 1,930			& ???	& 2153 \\ 
10,000 		& 			& ???	& 4576 \\ \hline
\end{tabular}
\end{center}
\caption{Decoding time with 32-threads for different stack configurations (sec)}
\label{tab:stack-configuration-time}
\end{table}

>>>>

We also note that distortion limit which constrains hypothesis extension is dependent on the hypothesis' coverage vector, $C$ \emph{and} the end position of most recent source word that has been translated, $e$. The distortion limit must be checked for every instance of a hypothesis and translation rule, Figure~\ref{algo:Hypothesis Expansion with Unsorted Stack}.
\begin{figure} [h]
\begin{algorithmic}
%\REQUIRE source sentence $s$, translation options
\FORALL{ $hypo$ in $stack_{|C|}$} 
  \FORALL{ translation rules}
      \IF {can-expand($C(hypo)$, $e(hypo)$, translation rule range)}
	\STATE expand hypo with translation rule $\rightarrow$ new hypo
	\STATE add new hypo to next stack
      \ENDIF
  \ENDFOR % { translation options}
\ENDFOR % { hypothesis in $stack_i$} 
\end{algorithmic}
\caption{Hypothesis Expansion with Unsorted Stack}
\label{algo:Hypothesis Expansion with Unsorted Stack}
\end{figure}
However, by separating hypotheses into \emph{'ministacks'} according to coverage and end position, the distortion limit only needs to be checked for each ministack, Figure~\ref{algo:Hypothesis Expansion with Sorted Stack}.
\begin{figure} [h]
\begin{algorithmic}
%\REQUIRE source sentence $s$, translation options
\FORALL{ $ministack_{C, e}$ in $stack_{|C|}$} 
  \FORALL{ translation rules}
    \IF {can-expand($C$, $e$, translation rule range)}
      \FORALL{ $hypo$ in $ministack_{C, e}$} 
	\STATE expand hypo with translation rule $\rightarrow$ new hypo
	\STATE add new hypo to next ministack
      \ENDFOR
    \ENDIF
  \ENDFOR % { translation options}
\ENDFOR % { hypothesis in $stack_i$} 
\end{algorithmic}
\caption{Hypothesis Expansion with Sorted Stack}
\label{algo:Hypothesis Expansion with Sorted Stack}
\end{figure}
We therefore looked at the effects of three stack configurations.
\begin{enumerate}
  \item coverage cardinality,
  \item coverage,
  \item coverage and end position of most recent translated source word.
\end{enumerate}
We therefore looked at the effects of three stack configurations.
\begin{enumerate}
  \item coverage cardinality,
  \item coverage,
  \item coverage and end position of most recent translated source word.
\end{enumerate}
Table~\ref{tab:stack-configuration-model-score} present the average model on the held out test set, while Table~\ref{tab:stack-configuration-time} presents the decoding time.
\begin{table}[h]
\small
\begin{center}
\begin{tabular}{|r|p{12mm}|p{12mm}|p{13mm}|} \hline
Pop-limit	& Coverage \newline cardinality	& Coverage	& Coverage \newline \& end pos \\ \hline
100  		& -8.64513 			& -8.64513	& -8.64513 \\
500		& -8.59563			& -8.59563 	& -8.59612 \\
1,000	 	& -8.58700			& -8.58700	& -8.5870 \\ 
5,000 		& -8.58165			& -8.58165	& -8.58098 \\ 
10,000 		& -8.58133			& -8.58133	& -8.58015 \\ \hline
\end{tabular}
\end{center}
\caption{Average model scores for different stack configurations}
\label{tab:stack-configuration-model-score}
\end{table}

\begin{table}[h]
\small
\begin{center}
\begin{tabular}{|r|p{12mm}|p{12mm}|p{13mm}|} \hline
Pop-limit	& Coverage \newline cardinality	& Coverage	& Coverage \newline \& end pos \\ \hline
100  		& 73 			& 75	& 72 \\
500		& 237			& 225 	& 229 \\
1,000	 	& 416			& ???	& 423 \\ 
5,000 		& 1,930			& ???	& 2153 \\ 
10,000 		& 3,619			& ???	& 4576 \\ \hline
\end{tabular}
\end{center}
\caption{Decoding time with 32-threads for different stack configurations (sec)}
\label{tab:stack-configuration-time}
\end{table}
